### 2018-11-25 Sections/cloud_quantum_computing.tex
tiny
minor
captionspacefig

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{distributed_search}
	\caption{Example of a quantum \textsc{MapReduce} protocol for implementing a distributed quantum search over four nodes. Each node performs a quantum search over the reduced space $x'$, concatenated with the identification number of the node, which recovers the full search-space $x$ across all the nodes collectively. This effectively partitions and allocates the search-space across the nodes, which implement their reduced searches in parallel. The net speedup provided by $M$ nodes operating in parallel scales as $O(\sqrt{M})$.}\label{fig:distributed_search}\index{Distributed quantum search algorithm}
\end{figure}

@@

To the contrary, unlike most quantum algorithms, whose power grows exponentially with the number of qubits (increasing returns\index{Increasing returns}), the distributed quantum search algorithm exhibits diminishing returns\index{Diminishing returns} with the degree of parallelisation -- the computational gain from adding one additional node to the network scales as,
\begin{align}
O\left(\sqrt{\frac{M+1}{M}}\right) &= O\left(\sqrt{1+\frac{1}{M}}\right),\nonumber\\
\lim_{M\to\infty} O\left(\sqrt{1+\frac{1}{M}}\right) &= O(1).
\end{align}
That is, increasing the number of nodes from 1 to 2 has far greater net gain than increasing them from 100 to 101. In fact, asymptotically, the gain from adding an additional node vanishes in the limit of a high degree of parallelisation.

>>>>

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{distributed_search}
	\captionspacefig \caption{Example of a quantum \textsc{MapReduce} protocol for implementing a distributed quantum search over four nodes. Each node performs a quantum search over the reduced space $x'$, concatenated with the identification number of the node, which recovers the full search-space $x$ across all the nodes collectively. This effectively partitions and allocates the search-space across the nodes, which implement their reduced searches in parallel. The net speedup provided by $M$ nodes operating in parallel scales as $O(\sqrt{M})$.}\label{fig:distributed_search}\index{Distributed quantum search algorithm}
\end{figure}

@@

To the contrary, unlike most quantum algorithms, whose power grows exponentially with the number of qubits (increasing returns\index{Increasing returns}), the distributed quantum search algorithm exhibits diminishing returns\index{Diminishing returns} with the degree of parallelisation -- the computational gain from adding one additional node to the network scales as,
\begin{align}
\sqrt{\frac{M+1}{M}},
\end{align}
which in the large $M$ limit goes to,
\begin{align}
\lim_{M\to\infty} \sqrt{\frac{M+1}{M}} = 1.
\end{align}
That is, increasing the number of nodes from 1 to 2 has far greater net gain than increasing them from 100 to 101. In fact, asymptotically, the gain from adding an additional node vanishes in the limit of a high degree of parallelisation.

### 2018-11-25 Sections/errors_in_quantum_networks.tex
More indexing
braket
captionspacefig

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{free_space_dispersion}
	\caption{Spot-size of an optical beam grows quadratically with distance from the source. If the beam is then collected via a camera with aperture area $A'$, any component of $A$ falling outside of $A'$ is effectively lost, yielding an effective loss channel with efficiency \mbox{$\eta = \frac{A'}{A} = \frac{A'}{\pi d^2 \tan^2\theta} = O\left(\frac{1}{d^2}\right)$}.} \label{fig:free_space_disp}
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{T2_time}
	\caption{Dephasing under continuous-time evolution, with characteristic decay rate given by the $T_2$-time. $p_\mathrm{no\,error}$ is the probability that the state is left unchanged, whereas \mbox{$1-p_\mathrm{no\,error}$} is the probability that it is replaced with the completely dephased state.}\label{fig:T2_time}
\end{figure}

@@

Let us consider this in detail. Consider the two-mode, two-photon state,
\begin{align}
\ket\psi_\mathrm{in} = \hat{A}^\dag_{\psi_1} \hat{B}^\dag_{\psi_2} \ket{0},
\end{align}
where $\hat{A}^\dag$ and $\hat{B}^\dag$ denote the mode operators for two spatial modes, with respective temporal distribution functions $\psi_1$ and $\psi_2$. Evolving this though a 50:50 (Hadamard) beamsplitter yields,
\begin{align}
\ket\psi_\mathrm{out} &= \hat{U} \ket\psi_\mathrm{in} \\
&= \frac{1}{2} \left[\hat{A}^\dag_{\psi_1}+\hat{B}^\dag_{\psi_1}\right]\left[\hat{A}^\dag_{\psi_2}-\hat{B}^\dag_{\psi_2}\right] \ket{0} \nonumber \\
&= \frac{1}{2} \left[\hat{A}^\dag_{\psi_1}\hat{A}^\dag_{\psi_2} - \hat{A}^\dag_{\psi_1}\hat{B}^\dag_{\psi_2} + \hat{A}^\dag_{\psi_2}\hat{B}^\dag_{\psi_1} - \hat{B}^\dag_{\psi_1}\hat{B}^\dag_{\psi_2}\right] \ket{0} \nonumber.
\end{align}
Post-selecting upon detecting a coincidence event (i.e one photon per mode), the conditional state is projected onto,
\begin{align}
\ket\psi_\mathrm{cond} = \frac{1}{2} \left[\hat{A}^\dag_{\psi_1}\hat{B}^\dag_{\psi_2} - \hat{A}^\dag_{\psi_2}\hat{B}^\dag_{\psi_1}\right] \ket{0}.
\end{align}
The probability of this coincidence event occurring is then given by the normalisation of the residual state,
\begin{align}
P_\mathrm{coincidence} &= \left| \bra\psi_\mathrm{cond} \ket\psi_\mathrm{cond} \right|^2 \nonumber \\
&= \frac{1}{2} - \frac{1}{2} \left| \int^\infty_{-\infty} \psi_1(t)\psi_2^*(t)\,dt\right|^2.
\end{align}

@@

\subsection{Phase-space} \index{Phase-space errors}

>>>>

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{free_space_dispersion}
	\captionspacefig \caption{Spot-size of an optical beam grows quadratically with distance from the source. If the beam is then collected via a camera with aperture area $A'$, any component of $A$ falling outside of $A'$ is effectively lost, yielding an effective loss channel with efficiency \mbox{$\eta = \frac{A'}{A} = \frac{A'}{\pi d^2 \tan^2\theta} = O\left(\frac{1}{d^2}\right)$}.} \label{fig:free_space_disp}
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{T2_time}
	\captionspacefig \caption{Dephasing under continuous-time evolution, with characteristic decay rate given by the $T_2$-time. $p_\mathrm{no\,error}$ is the probability that the state is left unchanged, whereas \mbox{$1-p_\mathrm{no\,error}$} is the probability that it is replaced with the completely dephased state.}\label{fig:T2_time}
\end{figure}

@@

Let us consider this in detail. Consider the two-mode, two-photon state,
\begin{align}
\ket{\psi_\mathrm{in}} = \hat{A}^\dag_{\psi_1} \hat{B}^\dag_{\psi_2} \ket{0},
\end{align}
where $\hat{A}^\dag$ and $\hat{B}^\dag$ denote the mode operators for two spatial modes, with respective temporal distribution functions $\psi_1$ and $\psi_2$. Evolving this though a 50:50 (Hadamard) beamsplitter yields,
\begin{align}
\ket{\psi_\mathrm{out}} &= \hat{U} \ket{\psi_\mathrm{in}} \\
&= \frac{1}{2} \left[\hat{A}^\dag_{\psi_1}+\hat{B}^\dag_{\psi_1}\right]\left[\hat{A}^\dag_{\psi_2}-\hat{B}^\dag_{\psi_2}\right] \ket{0} \nonumber \\
&= \frac{1}{2} \left[\hat{A}^\dag_{\psi_1}\hat{A}^\dag_{\psi_2} - \hat{A}^\dag_{\psi_1}\hat{B}^\dag_{\psi_2} + \hat{A}^\dag_{\psi_2}\hat{B}^\dag_{\psi_1} - \hat{B}^\dag_{\psi_1}\hat{B}^\dag_{\psi_2}\right] \ket{0} \nonumber.
\end{align}
Post-selecting upon detecting a coincidence event (i.e one photon per mode), the conditional state is projected onto,
\begin{align}
\ket{\psi_\mathrm{cond}} = \frac{1}{2} \left[\hat{A}^\dag_{\psi_1}\hat{B}^\dag_{\psi_2} - \hat{A}^\dag_{\psi_2}\hat{B}^\dag_{\psi_1}\right] \ket{0}.
\end{align}
The probability of this coincidence event occurring is then given by the normalisation of the residual state,
\begin{align}
P_\mathrm{coincidence} &= \left| \braket{\psi_\mathrm{cond}|\psi_\mathrm{cond}} \right|^2 \nonumber \\
&= \frac{1}{2} - \frac{1}{2} \left| \int^\infty_{-\infty} \psi_1(t)\psi_2^*(t)\,dt\right|^2.
\end{align}

@@

\subsection{Phase-space} \index{Phase-space!Errors}

### 2018-11-25 Sections/interconnecting_and_interfacing_quantum_networks.tex
Fixed up fig sizes for 1 col
QFT complete
minor
captionspacefig

\comment{More details and techniques here}

@@

\subsubsection{Superconducting qubits}\index{Superconducting qubits}\index{Quantum transducers}\index{Microwave qubits}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{microwave_qubits}
\caption{Schematic sketch of the interaction between superconducting qubits and microwave qubits. The superconducting qubits are in the entangled state \mbox{$\frac{1}{\sqrt{2}}(\ket{e,g} + \ket{g,e})$}, where $\ket{g}$ and $\ket{e}$ are the ground and excited states of the superconducting qubits. These are subjected to interact with the flying qubits, the microwave qubit (red dashed arrow). The photons become entangled and the output state of the photons are \mbox{$\frac{1}{\sqrt{2}}(\ket{H,V} + \ket{V,H})$}, where $\ket{H}$ and $\ket{V}$ are the horizontal and vertical polarisation modes respectively.}\label{fig:microwave_qubits}\index{Microwave qubits}
\end{figure}

@@

\begin{figure}[!htbp]
\if 3\pubmode
\includegraphics[clip=true, width=\textwidth]{quantum_transducer}
\else
\includegraphics[clip=true, width=0.475\textwidth]{quantum_transducer}
\fi
\caption{Block diagram for the quantum transducer. The quantum computer comprising superconducting qubits couples with the microwave qubit. The microwave qubit and the photonic qubit are coupled by a three-level system in which the energy difference between the levels correspond to both microwave and visible optical frequencies. The thick arrows denote the forward process, required to convert the microwave to optical frequencies, and the dashed arrows represent the reverse process, required at the receiving end to convert the optical frequency to a microwave frequency.}\label{fig:quantum_transducer}
\end{figure}

@@

\begin{figure}[!htbp]
\if 3\pubmode
\includegraphics[clip=true, width=\textwidth]{transducer_scheme_1}
\else
\includegraphics[clip=true, width=0.475\textwidth]{transducer_scheme_1}
\fi
\caption{Scheme for an opto-mechanics-based quantum transducer. There are two possible ways of converting microwaves. The final steps for the process in which acoustic modes are transported using waveguides is enclosed by a brown coloured box with dashed outlines labeled (a). Similarly the blue coloured box labeled (b) represents the scheme where phonons are converted to optical photons which are then transmitted via optical fibres. The initial few steps consisting of the superconducting qubit, transmission line resonator and microwaves are common to both processes.}\label{fig:opto_mechanics_transducer}\index{Opto-mechanical quantum transducer}
\end{figure}

@@

\begin{figure}[!htbp]
\if 3\pubmode
\includegraphics[clip=true, width=0.9\textwidth]{transducer_scheme_2}
\else
\includegraphics[clip=true, width=0.475\textwidth]{transducer_scheme_2}
\fi
\caption{The spin-ensemble-based quantum transducer. Microwave photons are converted to optical photons via a spin-ensemble.}\label{fig:spin_ens_transducer}\index{Spin-ensemble quantum transducer}
\end{figure}

>>>>

@@

\subsubsection{Superconducting qubits}\label{sec:superconducting_qubits}\index{Superconducting qubits}\index{Quantum transducers}\index{Microwave qubits}

@@

\begin{figure}[!htbp]
\if 2\pubmode
	\includegraphics[clip=true, width=0.475\textwidth]{microwave_qubits}
\else
\includegraphics[clip=true, width=0.7\textwidth]{microwave_qubits}
\fi
\captionspacefig \caption{Schematic sketch of the interaction between superconducting qubits and microwave qubits. The superconducting qubits are in the entangled state \mbox{$\frac{1}{\sqrt{2}}(\ket{e,g} + \ket{g,e})$}, where $\ket{g}$ and $\ket{e}$ are the ground and excited states of the superconducting qubits. These are subjected to interact with the flying qubits, the microwave qubit (red dashed arrow). The photons become entangled and the output state of the photons are \mbox{$\frac{1}{\sqrt{2}}(\ket{H,V} + \ket{V,H})$}, where $\ket{H}$ and $\ket{V}$ are the horizontal and vertical polarisation modes respectively.}\label{fig:microwave_qubits}\index{Microwave qubits}
\end{figure}

@@

\begin{figure}[!htbp]
\if 3\pubmode
\includegraphics[clip=true, width=\textwidth]{quantum_transducer}
\else
\includegraphics[clip=true, width=0.475\textwidth]{quantum_transducer}
\fi
\captionspacefig \caption{Block diagram for the quantum transducer. The quantum computer comprising superconducting qubits couples with the microwave qubit. The microwave qubit and the photonic qubit are coupled by a three-level system in which the energy difference between the levels correspond to both microwave and visible optical frequencies. The thick arrows denote the forward process, required to convert the microwave to optical frequencies, and the dashed arrows represent the reverse process, required at the receiving end to convert the optical frequency to a microwave frequency.}\label{fig:quantum_transducer}
\end{figure}

@@

\begin{figure}[!htbp]
\if 3\pubmode
\includegraphics[clip=true, width=\textwidth]{transducer_scheme_1}
\else
\includegraphics[clip=true, width=0.475\textwidth]{transducer_scheme_1}
\fi
\captionspacefig \caption{Scheme for an opto-mechanics-based quantum transducer. There are two possible ways of converting microwaves. The final steps for the process in which acoustic modes are transported using waveguides is enclosed by a brown coloured box with dashed outlines labeled (a). Similarly the blue coloured box labeled (b) represents the scheme where phonons are converted to optical photons which are then transmitted via optical fibres. The initial few steps consisting of the superconducting qubit, transmission line resonator and microwaves are common to both processes.}\label{fig:opto_mechanics_transducer}\index{Opto-mechanical quantum transducer}
\end{figure}

@@

\begin{figure}[!htbp]
\if 3\pubmode
\includegraphics[clip=true, width=0.9\textwidth]{transducer_scheme_2}
\else
\includegraphics[clip=true, width=0.475\textwidth]{transducer_scheme_2}
\fi
\captionspacefig \caption{The spin-ensemble-based quantum transducer. Microwave photons are converted to optical photons via a spin-ensemble.}\label{fig:spin_ens_transducer}\index{Spin-ensemble quantum transducer}
\end{figure}

### 2018-11-25 Sections/network_algorithms.tex
Formatting, algs
captionspacefig

In Table.~\ref{tab:net_alg_sum} we summarise the upcoming discussion on important network algorithms, and their associated complexities.

@@

\begin{figure}[!htbp]
\if 2\pubmode
\includegraphics[clip=true, width=0.475\textwidth]{dijkstra_example_long}
\else
\includegraphics[clip=true, width=0.7\textwidth]{dijkstra_example}
\fi
\caption{Example of Dijkstra's shortest-path algorithm for finding the shortest route from $A$ to $B$ (blue route), yielding a shortest route of distance 20 using 5 algorithmic steps. Initially (\mbox{$t=0$}) all nodes are designated a tentative distance of $\infty$ and marked as unvisited (blue vertices), except the starting node $A$, which is designated distance $0$ and visited (red vertices). At each step we choose the lowest cost path to a previously unexplored node (red edges). This updates the tentative distance of the newly-visited neighbour, which is now marked as visited. This is iterated until all nodes have been visited. Each node is visited exactly once.}\label{fig:dijkstra_eg}\index{Shortest-path algorithm}
\end{figure}

@@

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.35\textwidth]{constrained_shortest_path_long}
\caption{Example of a constrained shortest-path algorithm. Beginning with the initial graph we eliminate edges that do not satisfy imposed nearest-neighbour constraints. This is performed as a pre-processing stage. Then a usual shortest-path algorithm is applied to the reduced graph, yielding the optimal route subject to the required constraints.}\label{fig:constrained_shortest_path}
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[clip=true, width=\textwidth]{constrained_shortest_path}
\caption{Example of a constrained shortest-path algorithm. Beginning with the initial graph we eliminate edges that do not satisfy imposed nearest-neighbour constraints. This is performed as a pre-processing stage. Then a usual shortest-path algorithm is applied to the reduced graph, yielding the optimal route subject to the required constraints.}\label{fig:constrained_shortest_path}
\end{figure*}
\fi

@@

\begin{figure}[!hbtp]
\includegraphics[clip=true, width=0.475\textwidth]{vehicle_routing_alg}
	\caption{Example of the vehicle routing problem, the multi-user generalisation of the shortest-path problem, where the goal is to minimise the total cost across all users. Intuitively, because whenever individual shortest-paths intersect one must trial different prioritisations, the combinatorics of this grow exponentially with the number of competing users.}\label{fig:VRS}
\end{figure}

>>>>

In Tab.~\ref{tab:net_alg_sum} we summarise the upcoming discussion on important network algorithms, and their associated complexities.

@@

\begin{figure}[!htbp]
\if 2\pubmode
\includegraphics[clip=true, width=0.475\textwidth]{dijkstra_example_long}
\else
\includegraphics[clip=true, width=0.7\textwidth]{dijkstra_example}
\fi
\captionspacefig \caption{Example of Dijkstra's shortest-path algorithm for finding the shortest route from $A$ to $B$ (blue route), yielding a shortest route of distance 20 using 5 algorithmic steps. Initially (\mbox{$t=0$}) all nodes are designated a tentative distance of $\infty$ and marked as unvisited (blue vertices), except the starting node $A$, which is designated distance $0$ and visited (red vertices). At each step we choose the lowest cost path to a previously unexplored node (red edges). This updates the tentative distance of the newly-visited neighbour, which is now marked as visited. This is iterated until all nodes have been visited. Each node is visited exactly once.}\label{fig:dijkstra_eg}\index{Shortest-path algorithm}
\end{figure}

@@

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.35\textwidth]{constrained_shortest_path_long}
\captionspacefig \caption{Example of a constrained shortest-path algorithm. Beginning with the initial graph we eliminate edges that do not satisfy imposed nearest-neighbour constraints. This is performed as a pre-processing stage. Then a usual shortest-path algorithm is applied to the reduced graph, yielding the optimal route subject to the required constraints.}\label{fig:constrained_shortest_path}
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[clip=true, width=\textwidth]{constrained_shortest_path}
\captionspacefig \caption{Example of a constrained shortest-path algorithm. Beginning with the initial graph we eliminate edges that do not satisfy imposed nearest-neighbour constraints. This is performed as a pre-processing stage. Then a usual shortest-path algorithm is applied to the reduced graph, yielding the optimal route subject to the required constraints.}\label{fig:constrained_shortest_path}
\end{figure*}
\fi

@@

\begin{figure}[!hbtp]
\includegraphics[clip=true, width=0.475\textwidth]{vehicle_routing_alg}
	\captionspacefig \caption{Example of the vehicle routing problem, the multi-user generalisation of the shortest-path problem, where the goal is to minimise the total cost across all users. Intuitively, because whenever individual shortest-paths intersect one must trial different prioritisations, the combinatorics of this grow exponentially with the number of competing users.}\label{fig:VRS}
\end{figure}

### 2018-11-25 Sections/optical_routers.tex
captionspacefig

We will use the terminology that:
\begin{itemize}
	\item \textit{Ports}\index{Ports}: refers to the number of input and output optical modes in a device.
	\item \textit{Channels}\index{Channels}: refers to the number of simultaneous communications streams running in parallel through the device.
	\item \textit{Optical depth}\index{Optical!Depth}: is the number of primitive optical elements/devices an optical path traverses through the course of its trajectory from input to output.
	\item \textit{Directionality}\index{Directionality}: whether information is transferred in one or two directions.
	\item \textit{Switching time}\index{Switching time}: Time for the switch to get configured from one state to another state.
	\item \textit{Delay time}\index{Delay time}: time taken by signal to reach the output line of the switch from input.
	\item \textit{Throughput}\index{Throughput}: maximum data rate that can flow through the switch.
	\item \textit{Switching energy}\index{Switching energy}: energy needed for activating and deactivating the switch.
	\item \textit{Power dissipation}\index{Power dissipation}: energy dissipated per second in the process of switching.
	\item \textit{Insertion loss}\index{Insertion loss}: loss in signal power when the switch is connected.
	\item \textit{Crosstalk}\index{Crosstalk}: the power leaked to other lines.
\end{itemize}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{pockels_medium} \if 2\pubmode \\ \fi
\includegraphics[clip=true, width=0.475\textwidth]{kerrs_medium}
\caption{Dependence of refractive index on electric field in: Pockel's medium\index{Pockel's medium}, exhibiting linear electric field dependence; Kerr's medium\index{Kerr's medium}, exhibiting quadratic electric field dependence.}\label{fig:EOM_ref_index}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.35\textwidth]{AOM}
\caption{Acousto-optic modulators as a classically-controlled optical switch. The light signal is refracted depending on the applied sound wave.}\label{fig:AOM}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.25\textwidth]{AOM_energy_diagram}
\caption{Energy diagram for an acousto-optic modulator, based on Eq.~(\ref{eq:AOM_energy}). Energy and momentum must be conserved from the incident photon of energy $\hbar\omega$ and phonon of energy $\hbar\Omega$, yielding a scattered photon of energy $\hbar\omega_r$.}\label{fig:AOM_energy_diagram}
\end{figure}

>>>>

We will use the terminology that:
\begin{itemize}
	\item \textit{Ports}\index{Ports}: number of input and output optical modes in a device.
	\item \textit{Channels}\index{Channels}: number of simultaneous communications streams running in parallel through the device.
	\item \textit{Optical depth}\index{Optical!Depth}: number of primitive optical elements/devices an optical path traverses through the course of its trajectory from input to output.
	\item \textit{Directionality}\index{Directionality}: whether information is transferred in one (unidirectional) or two (bidirectional) directions.
	\item \textit{Switching time}\index{Switching time}: time for the switch to be reconfigured from one state to another.
	\item \textit{Delay time}\index{Delay time}: time taken by signal to reach the output line of the switch from input.
	\item \textit{Throughput}\index{Throughput}: maximum data rate that can flow through the switch.
	\item \textit{Switching energy}\index{Switching energy}: energy input required for activating and deactivating the switch.
	\item \textit{Power dissipation}\index{Power dissipation}: power dissipated during the process of switching.
	\item \textit{Insertion loss}\index{Insertion loss}: loss in signal power when the switch is connected.
	\item \textit{Crosstalk}\index{Crosstalk}: coupling to other optical modes.
\end{itemize}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{pockels_medium} \if 2\pubmode \\ \fi
\includegraphics[clip=true, width=0.475\textwidth]{kerrs_medium}
\captionspacefig \caption{Dependence of refractive index on electric field in: Pockel's medium\index{Pockel's medium}, exhibiting linear electric field dependence; Kerr's medium\index{Kerr's medium}, exhibiting quadratic electric field dependence. Graphs express qualitative behaviour only, hence no numbers are provided.}\label{fig:EOM_ref_index}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.35\textwidth]{AOM}
\captionspacefig \caption{Acousto-optic modulators as a classically-controlled optical switch. The light signal is refracted depending on the applied sound wave.}\label{fig:AOM}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.25\textwidth]{AOM_energy_diagram}
\captionspacefig \caption{Energy diagram for an acousto-optic modulator, based on Eq.~(\ref{eq:AOM_energy}). Energy and momentum must be conserved from the incident photon of energy $\hbar\omega$ and phonon of energy $\hbar\Omega$, yielding a scattered photon of energy $\hbar\omega_r$.}\label{fig:AOM_energy_diagram}
\end{figure}

### 2018-11-25 Sections/optical_stability_in_quantum_networks.tex
captionspacefig

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{wavepacket} \\
	\captionspacefig \caption{(top) A photonic wave-packet of the form of Eq.~(\ref{eq:wavepacket_modulated}), with Gaussian temporal envelope of width $\sigma$ (orange), shifted by a carrier frequency $\omega_0$ (blue).} \label{fig:HOM_vs_MZ}
\end{figure}

>>>>

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{wavepacket} \\
	\captionspacefig \caption{A photonic wave-packet of the form of Eq.~(\ref{eq:wavepacket_modulated}), with Gaussian temporal envelope of width $\sigma$ (orange), shifted by a carrier frequency $\omega_0$ (blue).} \label{fig:HOM_vs_MZ}
\end{figure}

### 2018-11-25 Sections/physical_architectures_for_quantum_computing.tex
captionspacefig

\begin{figure*}[!htpb]
	\includegraphics[clip=true, width=\textwidth]{weak_ck_parity_gate}
\caption{Construction of a two-mode, polarisation-encoded, photonic parity gate using an ancillary qubus coherent state $\ket\alpha$, mediating entangling photonic interactions between $\ket{\psi_a}$ and $\ket{\psi_b}$ via weak cross-Kerr non-linearities (denoted by the controlled-$\theta$ gates). The polarising beamsplitters\index{Polarising beamsplitters} are used to switch between polarisation and dual-rail encoding. The qubus is an optical channel, potentially across long distances over the quantum internet for performing distributed gates. The measurement $M$ is a homodyne measurement\index{Homodyne measurements}, which feedforwards an $X$-quadrature measurement outcome to a local phase correction. This gate could be used for preparing distributed photonic cluster states, a resource for universal quantum computation.}\label{fig:weak_ck_parity}	
\end{figure*}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{BS_2_photon_combinatorics}
\caption{A linear optics interferometer $\hat{U}$, fed with 2 single-photon inputs, one in each of the first two modes. To calculate the output amplitude of one photon in each of the modes 2 and 3, we sum the amplitudes of all possible paths consistent with that output. In this example there are only two such paths -- either both photons pass straight through, or they swap positions. This summation yields a \mbox{$2\times 2$} matrix permanent, given by Eq.~(\ref{eq:BS_2_ph_comb}).}\label{fig:BS_2_comb}	
\end{figure}

@@

\begin{figure}[!htbp]
\if 2\pubmode
	\includegraphics[clip=true, width=0.475\textwidth]{BS_3_photon_combinatorics}
\else
	\includegraphics[clip=true, width=0.6\textwidth]{BS_3_photon_combinatorics}
\fi
\caption{A linear optics interferometer $\hat{U}$, fed with 3 single-photon inputs, in modes 1, 2 and 3. To calculate the output amplitude of one photon in each of the modes 1, 2 and 3, we sum the amplitudes of all possible paths consistent with that output. This summation yields a \mbox{$3\times 3$} matrix permanent, given by Eq.~(\ref{eq:BS_3_ph_comb}).}\label{fig:BS_3_comb}	
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{artificial_atom_energy_levels}
\caption{The energy levels of: (a) a quantum oscillator; and, (b) an atomic system. The quantum oscillator exhibits equidistant separation between energy levels, whereas for the atomic system the energy levels are non-uniform.}\label{fig:artificial_atom_energy_levels}\index{Energy levels}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{superconducting_qubits}
\caption{Simplified circuits of the different kinds of superconducting qubits, namely the charge qubit, flux qubit and phase qubit. Below each circuit are their respective energy level diagrams.}\label{fig:superconductor_circuits}
\end{figure}

>>>>

\begin{figure*}[!htpb]
	\includegraphics[clip=true, width=\textwidth]{weak_ck_parity_gate}
\captionspacefig \caption{Construction of a two-mode, polarisation-encoded, photonic parity gate using an ancillary qubus coherent state $\ket\alpha$, mediating entangling photonic interactions between $\ket{\psi_a}$ and $\ket{\psi_b}$ via weak cross-Kerr non-linearities (denoted by the controlled-$\theta$ gates). The polarising beamsplitters\index{Polarising beamsplitters} are used to switch between polarisation and dual-rail encoding. The qubus is an optical channel, potentially across long distances over the quantum internet for performing distributed gates. The measurement $M$ is a homodyne measurement\index{Homodyne measurements}, which feedforwards an $X$-quadrature measurement outcome to a local phase correction. This gate could be used for preparing distributed photonic cluster states, a resource for universal quantum computation.}\label{fig:weak_ck_parity}	
\end{figure*}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{BS_2_photon_combinatorics}
\captionspacefig \caption{A linear optics interferometer $\hat{U}$, fed with 2 single-photon inputs, one in each of the first two modes. To calculate the output amplitude of one photon in each of the modes 2 and 3, we sum the amplitudes of all possible paths consistent with that output. In this example there are only two such paths -- either both photons pass straight through, or they swap positions. This summation yields a \mbox{$2\times 2$} matrix permanent, given by Eq.~(\ref{eq:BS_2_ph_comb}).}\label{fig:BS_2_comb}	
\end{figure}

@@

\begin{figure}[!htbp]
\if 2\pubmode
	\includegraphics[clip=true, width=0.475\textwidth]{BS_3_photon_combinatorics}
\else
	\includegraphics[clip=true, width=0.6\textwidth]{BS_3_photon_combinatorics}
\fi
\captionspacefig \caption{A linear optics interferometer $\hat{U}$, fed with 3 single-photon inputs, in modes 1, 2 and 3. To calculate the output amplitude of one photon in each of the modes 1, 2 and 3, we sum the amplitudes of all possible paths consistent with that output. This summation yields a \mbox{$3\times 3$} matrix permanent, given by Eq.~(\ref{eq:BS_3_ph_comb}).}\label{fig:BS_3_comb}	
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{artificial_atom_energy_levels}
\captionspacefig \caption{The energy levels of: (a) a quantum oscillator; and, (b) an atomic system. The quantum oscillator exhibits equidistant separation between energy levels, whereas for the atomic system the energy levels are non-uniform.}\label{fig:artificial_atom_energy_levels}\index{Energy levels}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{superconducting_qubits}
\captionspacefig \caption{Simplified circuits of the different kinds of superconducting qubits, namely the charge qubit, flux qubit and phase qubit. Below each circuit are their respective energy level diagrams.}\label{fig:superconductor_circuits}
\end{figure}
